%-------------------------
% Resume in Latex
% Author : Aiman Hakimi
% Website: https://github.com/aeyage/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[paperwidth=21cm,paperheight=35cm,margin=1in]{geometry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{Aiman Hakimi}{\Large Aiman Hakimi}} & \href{mailto:aimanhk@proton.me}{aimanhk@proton.me}\\
  \href{https://github.com/aeyage}{GitHub} $|$ 
  \href{https://www.linkedin.com/in/aeyage/}{LinkedIn} 
  & +6016-348-9982 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Science Malaysia}{Penang, Malaysia}
      {Bachelor of Computer Science (Hons.)(Intelligent Computing)}{Oct. 2021 - Present}

    \resumeSubheading
      {Negeri Sembilan Matriculation College}{Negeri Sembilan, Malaysia}
      {Matriculation Programme (Science Major - Module I); CGPA: (3.71/4.00)}{May. 2019 - Apr. 2020}
   \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google Developer Student Clubs USM}{Penang, Malaysia}
      {Advisory Board}{Sep. 2023 - Present}
      
    \resumeSubheading
      {Google Developer Student Clubs USM}{Penang, Malaysia}
      {Head Secretary; Core Team Member}{Sep. 2022 - Aug. 2023}
      
      \resumeItemListStart          
        \resumeItem{Documentation}
          {Managed all the official documents and paperwork and acted as mediator along with the Lead (GDSC local chapter leader) to facilitate communication with the University top management}
      \resumeItemListEnd

    \resumeSubheading
      {Say Hello to Web and Firebase}{Penang, Malaysia}
      {Head Secretary; GDSC USM Core Team Member}{Jun. 2023}
      \resumeItemListStart
        \resumeItem{Beginner-friendly Workshop}
          {A short workshop to introduce tech enthusiasts mainly comprising USM students to web development and Firebase Auth taught by a junior computer science student from USM who majors in software engineering. (HTML, CSS, Javascript, React, Firebase Authentication)}
      \resumeItemListEnd
    
    \resumeSubheading
      {KitaHack 2023, Google Developer Student Clubs Malaysia}{Subang Jaya, Malaysia}
      {Member of Secretarial}{Dec. 2022 - Mar. 2023}
      \resumeItemListStart
        \resumeItem{Google Technologies Exposure}
          {GDSC members across all chapters to have equal access to learn and build their solutions to solve one or more of the 17 SDGs of the United Nations, to gain expert mentorship and feedback prior to submission to the 2023 Solution Challenge which is Google's global annual contest. (Flutter, TensorFlow, Firebase etc.)}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Study Jam with Kaggle}{Penang, Malaysia}
      {Head Secretary; GDSC USM Core Team Member}{Nov. 2022 - Dec. 2023}
      \resumeItemListStart
        \resumeItem{Peer-to-peer ML Learning Opportunity}
          {Hands-on Machine Learning experience. The event was tailored to cater beginner, intermediate and advanced AI enthusiasts. (CNN for Image Classification, BERT Model for Sentiment Analysis)}
      \resumeItemListEnd

    \resumeSubheading
      {GitHub for Dummies}{Penang, Malaysia}
      {Head Secretary; GDSC USM Core Team Member}{Dec. 2022}
      \resumeItemListStart
        \resumeItem{Novice Crash Course}
          {An introductory course to give exposure to the freshmen of USM about the importance of version control using Git and the fundamental features of GitHub.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{USModuleHub}
      {A one-stop open-source college course catalogue, module search platform to seamlessly help plan students' timetables and learn about the different modules offered in University of Science Malaysia. It also serves as a complete knowledge bank of USM modules by providing useful module-related information such as community-driven module reviews and discussions.}
    
    \resumeSubItem{N-gram and PoS Tagging of DBS Banking Performance}
      {A natural language processing model aims to study the sentiment and text analysis of DBS Bank performance feedback by performing n-gram and part-of-speech tagging on a total of 107 DBS consumer reviews scrapped from external review sites.}
    
    \resumeSubItem{Malay Word Prediction Using Word2vec Embedding}
      {A natural language processing sentiment prediction model for text in Malay Language. It is trained with a deep learning neural network to construct an end-to-end Malay word prediction model.}
    
    \resumeSubItem{3D Sierpiński Gasket Ident Programme}
      {A graphical programme to create an animation that is regarded as a TV Ident (an animated logo which shows branding of a TV channel).}
    
    \resumeSubItem{Cervical Cancer Risk Classification}
      {A machine learning model for cervical cancer classification based on patient's risk factors. This is to help improve diagnosis of cervical cancer in patients as machine learning can be useful to provide informed data-driven decision-making in healthcare sector.}
      
    \resumeSubItem{Wine Quality Indicator}
      {A machine learning model to determine which physiochemical properties make a wine 'good'. It experimented with 3 algorithms namely k-NN, SVM, and Decision Tree. (Pandas, NumPy, Matplotlib, Seaborn)}

    \resumeSubItem{Wheel of Fortune}
      {A java project that recreates the classic game of Wheel of Fortune built as a project of Integrated Software Development Workshop module at USM. It demonstrates the use of OO Design Patterns. (Java, JavaFX)}

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
        \textbf{Programming Languages}{: Python, R, C++, Java, SQL, Javascript}
   }
   \item{
        \textbf{Technologies}{: Natural Language Toolkit, Tensorflow/ Keras, Scikit-Learn, Word2vec, WebGL, LaTeX, Three.js, Tailwind CSS, Boostrap, Livewire, Laravel, MySQL, React}
   }
   \item{
        \textbf{Languages}{: English, Malay, Japanese, Spanish}
   }
 \resumeSubHeadingListEnd

%---------------------------
\end{document}
